Addition and removal energies of circular quantum dots

### 2017-04-06 Manuscript/paper.tex
Update paper

We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.  Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.  All such results show good agreement with one another.  We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the slightly more expensive EOM calculations.  Moreover, IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost methods such as FCI, allowing exploration of much higher number of particles than would otherwise be possible.

@@

We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.  A new technique developed by T. D. Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at much lower cost.  Implementing this approach would be beneficial as it would allows us to study the accuracy and convergence of other possibly more sensitive observables.

@@

Eventually, we hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.

>>>>

We have demonstrated calculations of ground state, addition, and removal energies of two-dimensional circular quantum dots using a variety of many-body methods: ranging from the basic Hartree-Fock method, to more sophisticated combinations of IM-SRG, CC, QDPT and/or EOM.  Many closed-shell quantum dot systems have been explored, ranging from 2 to 56 particles and frequencies between 0.1 and 1.0.  All such results show good agreement with one another.

We note that the HF + IM-SRG + QDPT combination provides a reasonable moderate-cost approach to the calculation of addition and removal energies for many systems in comparison to the somewhat more expensive and complicated EOM calculations.  Both IM-SRG and CC are reasonably accurate compared to the near-exact but factorial-cost FCI method, allowing exploration of much higher number of particles than would otherwise be possible.  EOM-IM-SRG does have more flexibility over perturbative approaches: in particular, it could be more readily used to construct excited states \cite{2016arXiv161100661P}, which is more difficult for methods such as DMC.

@@

We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.  A new technique developed by T. D. Morris \cite{PhysRevC.92.034331} uses an alternative approach that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over coupled cluster methods.  Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.

The IM-SRG method can be extended to support multiple reference states (multi-reference IM-SRG or simply MR-IM-SRG) \cite{PhysRevLett.110.242501,PhysRevC.90.041302} through the generalized normal ordering formalisms \cite{doi:10.1063/1.474405}, which opens the possibility of calculating quantum systems that are far from the magic numbers (open-shell systems).  This is a territory that few many-body methods can tackle and is one of the major strengths of the IM-SRG approach.

By transforming of the operator-SRG rather than the wave function, IM-SRG is more amenable to the construction of softened \textit{effective interactions} than CC \cite{Hergert2016165}.  Such interactions can be used to lower the cost of other methods such as configuration interaction (CI), also known as \textit{shell model} in nuclear physics.

@@

We hope to apply these theoretical and technical enhancements not only to the study of quantum dots, but to studies of nuclear and atomic systems, opening up an even greater range of applications.
